\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{times}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }



\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}

    


\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Adarsh Yogesh Pai}}\\
	Dallas-Fort Worth, Texas $\cdot$ adarsh9pai@gmail.com $\cdot$ 682.551.2698 $\cdot$ www.adarshpai.com\\
\end{center}

%==== Experience ====%
\header{Education}
\textbf{University of Texas at Arlington}\hfill Arlington, Texas\\
B.S. Computer Science \textit{GPA: 3.564} \hfill August 2017 - May 2021\\

\begin{itemize} \itemsep 1pt
	\item CSE GPA: 4.0
	\item Relevant Coursework: Fundamentals of Software Engineering, Algorithms and Data Structures, Object Oriented Programming, Discrete Structures, Computer Organization and Assembly, Linear Algebra.
	\item Member of the Honors College.
	\item Maverick Academic Scholarship(\$5000 per annum) and Out of State tuition waiver
         \item Peer Academic Leader (August 2018 - Present): Instructor for UNIV-EN 1131(Computer Science) and UNIV-LA 1000(Music).
\end{itemize}
\vspace{2mm}
\header{Experience}
\vspace{1mm}

\textbf{Heracleia Human-Centered Computing Lab} \hfill Arlington, Texas\\
\textit{Undergraduate Research Assistant} \hfill May 2018 | Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Improved Tensorflow based hand detector to streamline building datasets using OpenCV.
	\item Currently working on developing VR simulations for immersive storytelling.
	\item Primarily work with Python, OpenCV and C\#.
\end{itemize}

\textbf{Emerson Electric} \hfill Mumbai, India\\
\textit{Summer Intern, Information Technology} \hfill June 2017 | July 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed an internal web-based application to optimize scheduling and improve operational effectiveness.
	\item Primarily worked with PHP and Postgres.
\end{itemize}


\vspace{2mm}

\header{Projects}
{\textbf{Dostavi}} August 2018 - Present \hspace{1mm} Do not want to pay for international shipping for small parcels? Use Dostavi, a peer-to-peer solution to find travelers to deliver packages to places across the world. 
\begin{itemize}
\item Currently developing backend API and setting up basic frontend interface. Targeted finish time: December 2018.
\item \textit{Express, React, Mongo, Passport, Bulma} 
\end{itemize}
\vspace*{2mm}
{\textbf{Clime}} January 2018 \hspace{1mm} Get real-time weather updates, ATMs, Hospitals and Shelters near you at times of emergency.
\begin{itemize}
\item Developed Webhook for Facebook Messenger based chatbot. Used the OpenWeatherMap Weather API. Deployed Webhook to Heroku.
\item \textit{Express, Heroku, Facebook Messenger}
\end{itemize}
\textbf{Minor Projects} Repositories for university coursework, public projects and experiments with APIs. 
\begin{itemize}
\item GitHub: https://www.github.com/adarsh9pai
\end{itemize}
\vspace{2mm}

\header{Languages and Frameworks}
\begin{itemize}
\item Skilled: Python, C, JavaScript, NodeJs
\item Comfortable: C++, \LaTeX
\item Acquainted: Java, SQL, PHP
\item Frameworks: NumPy, Pandas, Scikit-Learn, Express, Flask, React, Bulma
\end{itemize}

\vspace{2mm}

\header{Extra Curricular Involvement}
\begin{itemize}
\item Election Supervisory Board, Student Government (September 2017 - May 2018)
\end{itemize}
\vspace{1mm}
\end{document}
